For achieving the basic goals, the estimated working time for each group member is 133.3 hours, and altogether for
all three members approximately 400 working hours. According to TEK (the largest organization for academic engineers
in Finland), the recommended salary for a starting salary for an M. Sc. (Tech.) is 3980€ in a month. There are 
approximately 172 working hours in one month, which results in 23.14€/hour. Thus, if we assume that the project
members would be starting their working careers in some company in Finland, the project would cost approximately
9256€ altogether.

For the advanced goal, the estimated working time for each group member is 160 hours, and altogether for all three
members approximately 480 working hours. Based on the aforementioned assumptions, the project would cost
approximately 11 107€ for achieving both the basic and the advanced goal.

The two clients are using approximately 30 minutes for each remote meeting which occurs every Friday. In addition,
if it is estimated that the clients both use approximately 30 minutes for the project each week outside the meeting
time, this gives an additional two working hours each week for the clients. Altogether, this leads to approximately
28 working hours for the clients. If an estimate of the salaries of the clients would be e.g. 5000€ a month, then
their input to the project would cost approximately 814€. Therefore, an estimate of the cost for the project would
be 10 070€ for only the basic goal, and 11 921€ for the basic goal and the advanced goal.