\section{Definition of objectives}

The objectives of different interest groups (project members, client and other
groups)
List here all possible goals you have set up with your client. Justify which
achievements are needed to receive the credits (and possibly, which extra
achievements give some extra credits).
Technical objectives (if applicable)
The required and unwanted properties of the objectives

The project objectives are divided into separate categories called basic and advanced goals. The separate goals are planned to make sure atleast the minimal wanted result for the project is achieved. If there is still time left to work on the project after the basic requirements are met the tasks defined in the advanced goal will be worked on. 

\section{The basic goal}

The basic goal is the minimal wanted result for the project. The basic goal requirements are planned so that each project member gains 5 credits for the project work. One credit amounts to 26+2/3 working hours. This means that the work spent on the basic goal will be approximately 133.3 hours for each project member. 

The objectives of the basic goal are as follows

\begin{itemize}
	\item Project initialization and planning
	\item Preliminary study of open source video detection methods that could be applied in the project
	\item Designing the scenes that are to be recorded using a 360 video camera and the integrated microphone array
	\item Recording the designed scenes
	\item Developing a set of python scripts for handling the video data frames (basic data handling methods for video)
	\item Developing a set of python scripts for applying object detection for the video data frames
	\item Developing a method for outputting the detected visual objects, their locations and the time interval of detection to be used together with spatial audio detection
	\item Testing the developed video handling scripts with the recorded video data
	\item Developing a method for outputting the detected sound events, their locations and the time interval of detection to be used together with spatial audio detection
	\item Manually mapping visual object labels with the sound event labels to be used for automated annotation
	\item Documenting (this includes the final report and the presentations)
	\item Testing the method against manual annotation
\end{itemize} 

\section{The advanced goal}

The advanced goal is meant to be worked on in case the basic goal is achieved and there is still time for further development. The advanced goal requirements are planned so that each project member gains 6 credits for the project work. This will amount to a total of 160 hours of work for each project member. 

The objectives of the advanced goal are as follows

\begin{itemize}
	\item Everything listed under the basic goal requirements
	\item Designing more complicated scenes to be recorded and testing the system with the
	\item Further developing the video detection part of the application so that different detection models could be used dynamically (as configured by the user)
	\item Testing if the use of tracking algorithms could be used to further improve the accuracy of the application (if needed)
	\item Developing a graphical user interface for the mapping of visual object labels and sound event labels
\end{itemize} 

\section{Deliverables}

The deliverables for the project will be as this project plan document, the final report of the project work, the presentations given during the course and the source codes of the developed application. 